Analyzing X-ray images in Python with scikit-image

### 2016-08-22 skimage_tomo.tex
Minor edits

    \texttt{scikit-image} is an open-source image processing toolkit for
    the Python language that supports a large variety of file formats and
    is compatible with 2-D and 3-D images. The toolkit exposes a simple
    programming interface, with thematic modules grouping functions
    according to their purpose, such as image restoration, segmentation,
    and measurements. \texttt{scikit-image} users benefit from a rich
    scientific Python ecosystem that contains many powerful libraries for
    tasks such as visualization or machine learning.
    \texttt{scikit-image} combines a gentle learning curve, versatile
    image processing capabilities, and the scalable performances required
    for the high-throughput analysis of X-ray imaging data.

@@

Several software applications and libraries are available to synchrotron
users to process their images. ImageJ \citep{Abramoff2004, Schneider2012}
and its distribution Fiji \citep{Schindelin2012} is a popular tool for
2-D and 3-D images, thanks to its intuitive menus and graphical tools,
and the wealth of plugins contributed by a vivid community
\citep{Schindelin2015}. For 3-D images, commercial tools such as Avizo 3D
software (TM) are appreciated for an intuitive graphical pipeline and
advanced 3D visualization. Alternatively, the use of a programming
language gives finer control, a better reproducibility and more
possibilities, provided classical processing algorithms can be called
from libraries -- thereby limiting the complexity of the programming task
and the risk of bugs. Matlab (TM) and its image processing toolbox are
popular in the academic community of computer vision and image
processing. The Python language is widely used in the scientific world
and in synchrotron facilities. As a general-purpose language, Python is
used in synchrotrons to control device servers \citep{pytango}, to access
raw data of X-ray detectors \citep{Knudsen2013}, to reconstruct
tomography volumes from radiographs \citep{Gursoy2014, Mirone2014}, and
in data processing packages for macromolecular cristallography
\citep{Adams2010}, azimuthal integration of diffraction data
\citep{Ashiotis2015}, or fluorescence analysis \citep{pymca}.

>>>>

    \texttt{scikit-image} is an open-source image processing toolkit for
    the Python language that supports a large variety of file formats and
    is compatible with 2-D and 3-D images. The toolkit exposes a simple
    programming interface, with thematic modules grouping functions
    according to their purpose, such as image restoration, segmentation,
    and measurements. \texttt{scikit-image} users benefit from a rich
    scientific Python ecosystem that contains many powerful libraries for
    tasks such as visualization or machine learning.
    \texttt{scikit-image} combines a gentle learning curve, versatile
    image processing capabilities, and the scalable performance required
    for the high-throughput analysis of X-ray imaging data.

@@

Several software applications and libraries are available to synchrotron
users to process their images. ImageJ \citep{Abramoff2004, Schneider2012}
and its distribution Fiji \citep{Schindelin2012} is a popular tool for
2-D and 3-D images, thanks to its intuitive menus and graphical tools,
and the wealth of plugins contributed by a vivid community
\citep{Schindelin2015}. For 3-D images, commercial tools such as Avizo 3D
software (TM) are appreciated for an intuitive graphical pipeline and
advanced 3D visualization. Alternatively, the use of a programming
language gives finer control, better reproducibility, and more complex analysis
possibilities, provided classical processing algorithms can be called
from libraries -- thereby limiting the complexity of the programming task
and the risk of bugs. Matlab (TM) and its image processing toolbox are
popular in the academic community of computer vision and image
processing. The Python language is widely used in the scientific world
and in synchrotron facilities. As a general-purpose language, Python is
used in synchrotrons to control device servers \citep{pytango}, to access
raw data of X-ray detectors \citep{Knudsen2013}, to reconstruct
tomography volumes from radiographs \citep{Gursoy2014, Mirone2014}, and
in data processing packages for macromolecular cristallography
\citep{Adams2010}, azimuthal integration of diffraction data
\citep{Ashiotis2015}, or fluorescence analysis \citep{pymca}.
